---
title: "Testing cloning"
output:
  html_document: default
---
In this notebook, we check if the cloning function works, and how to use it. 
To do so, we set the mating system to cloning (2), and we change the number of clone: mating_proportion (1 mean only clone and 0 only sexual reproduction). 
We then check in the Phenotype that the right proportion of individual has no father. 


###loading package and setting minimal simulation
```{r}
devtools::load_all(pkg="../test_quantinemo2/RQuantiNemo")
my_sim.base = new("simulation",sim.dir = "cloning/")
```

### Loop over cloning proportion
```{r}
my_sim = my_sim.base
my_sim <- setParameter(my_sim,"mating_system",2)
my_sim <- setParameter(my_sim,"patch_capacity",1000)
my_sim <- setParameter(my_sim,"generations",5)

my_sim <- setParameter(my_sim,"quanti_loci",1)
my_sim <- setParameter(my_sim,"quanti_save_phenotype ",2)

for(prop in seq(0,1,0.1)){
  my_sim <- setParameter(my_sim,"mating_proportion",prop)
  success <- run(my_sim)
  stopifnot(success=TRUE)
  Pheno <- loadPheno(my_sim)
  prop.q <- sum(as.character(Pheno$V7)=="NaN")/length(Pheno$V7)
  cat("expected: ", prop, "\n", "QuantiNemo: ", prop.q, "\n \n")
  stopifnot(abs(prop.q - prop) < 0.05)
}
```
