---
title: "density dependance of the migration rate"
output:
  html_document: default
---

##Introduction
The goal of this notebook is to describe and test the new implementation of the density dependance migration's rate.   
The migration rate can now be selected amoung three models. This is set by the parameter "migration_rate_model"
 
 * migration_rate_model = 0. Rate is flat and given by the parameter dispersal_rate.
 * migration_rate_model = 1. Rate follow the law $m\frac{e*(N-K(1-\exp(-N/K)))}{N}$, where $N$ is the number of individual before dispersal, $K$ the carrying capacity of the patch and $m$ the dispersal rate. The rate depend on the density of the patch and reach a capacity of m (set by the parameter dispersal_rate) for d = 1
 * migration_rate_model = 1.Rate follow the law $\frac{(N-K(1-\exp(-N/K)))}{N}$. The rate is adjusted so that the number of migrant allow the occupation after dispersal to be smaller than the patch_capacity. 

To visualize the behaviour, we use the following meta-pop. We use two patch, one is partially filled and the other one is complitely empty. We then simply check the number of people in the first (remaining people) and second patch (emigrant) after one generation.

### Setting general parameter for the simulaiton
```{r}
devtools::load_all(pkg="../RQuantiNemo")
parameters = list(
  "generations" = 2,
  "mating_nb_offspring_model"=1, 
  "patch_capacity" = 50,
  "replicates" = 10,
  "patch_number" = 2,
  "stat" = "{adlt.nbInd_p}"
)
my_sim <- new("simulation", parameters = parameters)
```

## Simulation for a flat migration rate. 
#### Loop over the number of initial individual in the first patch before dispersal
```{r}
my_sim <- setParameter(my_sim, "dispersal_rate", 0.2)
migrant = rep(0,200)
stay = rep(0,200)

for(i in 1:200){
  my_sim <- setParameter(my_sim, "patch_ini_size", paste("{", as.character(i)," 0}", collapse = ""))
  run(my_sim, verbose = F)
  stat <- loadStat(my_sim)
  migrant[i] <- stat$adlt.nbInd_p2[2]
  stay[i] <- stat$adlt.nbInd_p1[2]
}
```

#### Ploting the result
```{r}
plot(migrant, type = "l", col = "blue", lwd = 2,ylim = c(0,100), xlab = "Initial pop", ylab = "final pop")
lines(stay, col = "red", lwd = 2)
legend("topleft",legend = c("Emigrant","Remaining Ind."),
lty=c(1,1),
lwd=c(2.5,2.5),
col=c("blue","red")) 
```

#### Test
```{r}
migrant.th <- seq(1,200,1)*0.2
stay.th <-  seq(1,200,1)*(1-0.2)
migrant.diff <-  migrant - migrant.th
stay.diff <-  stay - stay.th
stopifnot(sum(stay.diff^2) < 1000)
stopifnot(sum(migrant.diff^2) < 1000)
```


## Density dependant dispersal rate model 1
### Simulation for a density dependant dispersal rate
#### Loop over the number of initial individual in the first patch before dispersal
```{r}
my_sim <- setParameter(my_sim, "dispersal_rate", 0.2)
my_sim <- setParameter(my_sim, "dispersal_rate_model", 1)
migrant = rep(0,200)
stay = rep(0,200)

for(i in 1:200){
  my_sim <- setParameter(my_sim, "patch_ini_size", paste("{", as.character(i)," 0}", collapse = ""))
  run(my_sim, verbose = F)
  stat <- loadStat(my_sim)
  migrant[i] <- stat$adlt.nbInd_p2[2]
  stay[i] <- stat$adlt.nbInd_p1[2]
}
```

#### Ploting the result
```{r}
plot(migrant, type = "l", col = "blue", lwd = 2,ylim = c(0,100), xlab = "Initial pop", ylab = "final pop")
lines(stay, col = "red", lwd = 2)
lines(rep(50,200), col = "black", lwd = 1, lty = 2)
legend("topleft",legend = c("Emigrant","Remaining Ind.", "Carrying capacity"),
lty=c(1,1,2),
lwd=c(2.5,2.5),
col=c("blue","red", "black")) 
```
#### Test
```{r}
x = seq(1,200,1)
migrant.th <- exp(1)*(x - 50*(1-exp(-x/50)))*0.2
stay.th <- x-exp(1)*(x - 50*(1-exp(-x/50)))*0.2
migrant.diff <-  migrant - migrant.th
stay.diff <-  stay - stay.th
stopifnot(sum(migrant.diff^2) < 1000)
stopifnot(sum(stay.diff^2) < 1000)
```


## Migration dependant rate, model 2 (saturation of the # of migrant)
#### Loop over the number of initial individual in the first patch before dispersal
This does probably not make much sens. Basically, when saturation of the patch is reach, half of the surnumerous individual leave and the other half stay. 

```{r}
my_sim <- setParameter(my_sim, "dispersal_rate", 0.1) #should have no influence whatsoever
my_sim <- setParameter(my_sim, "dispersal_rate_model", 2)
migrant = rep(0,200)
stay = rep(0,200)
for(i in 1:200){
  my_sim <- setParameter(my_sim, "patch_ini_size", paste("{", as.character(i)," 0}", collapse = ""))
  run(my_sim, verbose = F)
  stat <- loadStat(my_sim)
  migrant[i] <- stat$adlt.nbInd_p2[2]
  stay[i] <- stat$adlt.nbInd_p1[2]
}
```


#### Ploting the result
```{r}
plot(migrant, type = "l", col = "blue", lwd = 2,ylim = c(0,100), xlab = "Initial pop", ylab = "final pop")
lines(stay, col = "red", lwd = 2)
lines(rep(50,200), col = "black", lwd = 1, lty = 2)
legend("topleft",legend = c("Emigrant","Remaining Ind.", "Carrying capacity"),
lty=c(1,1,2),
lwd=c(2.5,2.5),
col=c("blue","red", "black")) 
```

#### Test
```{r}
x = seq(1,200,1)
migrant.th <-(x - 50*(1-exp(-x/50)))
stay.th <- ( 50*(1-exp(-x/50)))
migrant.diff <-  migrant - migrant.th
stay.diff <-  stay - stay.th
stopifnot(sum(migrant.diff^2) < 1000)
stopifnot(sum(stay.diff^2) < 1000)
```
