---
title: "density dependance of the migration rate"
output: html_document
---

The goal of this notebook is to test the density dependance of the migration rate. To check this, we use the following meta-pop. We use two patch, one is partially filled and the other one is complitely empty. We then simply check the number of people in the first (remaining people) and second patch (emigrant) after one generation.

##set general parameters and loading package
```{r}
devtools::load_all(pkg="../RQuantiNemo")
```


```{r}
parameters = list(
  "generations" = 3,
  "patch_capacity" = 100,
  "mating_nb_offspring_model" = 1,
  "replicates" = 100,
  "dispersal_rate" = 0.5,
  "patch_number" = 2,
  "patch_ini_size" = "{50 0}",
  "stat" = "{adlt.nbInd_p}",
  "dispersal_k_max_growth" = 0.5,
  "dispersal_k_growth_rate" = 20
)
my_sim <- new("simulation", parameters = parameters)
  run(my_sim, verbose = F)
```

##result
#### Loop over the number of initial individual in the first patch before dispersal
```{r}
migrant = rep(0,100)
stay = rep(0,100)

for(i in 1:100){
  my_sim <- setParameter(my_sim, "patch_ini_size", paste("{", as.character(i)," 0}", collapse = ""))
  run(my_sim, verbose = F)
  stat <- loadStat(my_sim)
  migrant[i] <- stat$adlt.nbInd_p2[2]
  stay[i] <- stat$adlt.nbInd_p1[2]
}
```

#### Ploting the result and comparing to theoretical value
```{r}
plot(migrant, type = "l", col = "blue", lwd = 2)
lines(x-plogis(x/100,0.5,1/20)*x*0.5, col = "black")
lines(plogis(x/100,0.5,1/20)*x*0.5, col = "black")

lines(stay, col = "red", lwd = 2)
x = seq(1,100,1)
legend("topleft",legend = c("Emigrant","remaining pop","theoretical"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red", "black")) # gives the legend lines the correct color and width
dist <-  plogis(x/100,0.5,1/20)*x*0.5 - migrant
stopifnot(sum(dist*dist)<50)

```
  
  