---
title: "Check extinction"
output:
  html_document: default
---
The goal of this notebook is to check if extinction rate works and is what is expected.
To do so, we create a meta-population with a lot of patch, and count the number of disapearance over a long period. 


### loading package and setting minimal simulation
```{r}
devtools::load_all(pkg="../RQuantiNemo")
my_sim.base = new("simulation",sim.dir = "extinction/")
```

```{r}
n.iter = 1000
n.patch = 100
patch.capacity = 100
```


```{r}
my_sim.base  <- setParameter(my_sim.base,"generations",n.iter)
my_sim.base  <- setParameter(my_sim.base,"patch_capacity",patch.capacity)
my_sim.base  <- setParameter(my_sim.base,"patch_number",n.patch)
my_sim.base  <- setParameter(my_sim.base,"stat","{adlt.nbInd_p }")
my_sim.base  <- setParameter(my_sim.base,"mating_nb_offspring_model",0)
my_sim.base  <- setParameter(my_sim.base,"dispersal_model",0)
my_sim.base  <- setParameter(my_sim.base,"dispersal_rate",0.5)
my_sim.base  <- setParameter(my_sim.base,"patch_ini_size",patch.capacity)
```



##Result
### Extinction without any repopulation
#### Launching simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name <-  "no_repopulation"
my_sim  <- setParameter(my_sim,"extinction_rate",0.2)
success <- run(my_sim, verbose = FALSE)
```
#### Checking rate
```{r}
Qn <- loadStat(my_sim)
Qn <- as.matrix(Qn[-1, 3:102])
computed.rate = sum(Qn ==0)/length(Qn)
print(computed.rate)
stopifnot(sum(Qn ==0) > qbinom(0.005,999*100,0.2))
stopifnot(sum(Qn ==0) < qbinom(0.995,999*100,0.2))
```

###same with different recombination rate
```{r}
my_sim = my_sim.base
my_sim@sim.name <-  "no_repopulation"
my_sim  <- setParameter(my_sim,"extinction_rate",0.6)
success <- run(my_sim, verbose = FALSE)
```
#### Checking rate
```{r}
Qn <- loadStat(my_sim)
Qn <- as.matrix(Qn[-1, 3:102])
computed.rate = sum(Qn ==0)/length(Qn)
print(computed.rate)
stopifnot(sum(Qn ==0) > qbinom(0.005,999*100,0.6))
stopifnot(sum(Qn ==0) < qbinom(0.995,999*100,0.6))
```

### Extinction with repopulation with fixed number of individual
#### Launching simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name <-  "absolute_repopulation"
my_sim  <- setParameter(my_sim,"extinction_rate",0.1)
my_sim  <- setParameter(my_sim,"extinction_rate_survival",10)
success <- run(my_sim, verbose = FALSE)
```

#### Checking rate
```{r}
Qn <- loadStat(my_sim)
Qn <- as.matrix(Qn[-1, 3:102])
computed.rate = sum(Qn ==10)/length(Qn)
print(computed.rate)
stopifnot(sum(Qn == 10) > qbinom(0.005,999*100,0.1))
stopifnot(sum(Qn == 10) < qbinom(0.995,999*100,0.1))
```

### Extinction with repopulation with percentage of previous population
#### Launching simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name <-  "relative_repopulation"
my_sim  <- setParameter(my_sim,"extinction_rate",0.05)
my_sim  <- setParameter(my_sim,"extinction_rate_survival",0.1)
success <- run(my_sim, verbose = FALSE)
```

#### Checking rate
```{r}
Qn <- loadStat(my_sim)
Qn <- as.matrix(Qn[-1, 3:102])
sum.pos <-  sum(Qn < 20 )
computed.rate = sum.pos/length(Qn)
print(computed.rate)
stopifnot(sum.pos > qbinom(0.005,999*100,0.05))
stopifnot(sum.pos < qbinom(0.995,999*100,0.05))
```