---
title: "Testing the femal sex allocation"
output:
  html_document: default
---

This notebook test the femal sex allocation. If we have a trait which give us the fem_sex_allocation, we expect this trait to converge toward 0.5. We observe a very slight difference, but not as big as what is expected. Why?

### loading package and setting minimal simulation
```{r}
devtools::load_all("../RQuantiNemo")
my_sim.base = new("simulation",sim.dir = "female_sex_allocation/")
```

```{r}
n.iter = 500
patch.capacity = 100
```


```{r}
my_sim.base  <- setParameter(my_sim.base,"generations",n.iter)
my_sim.base  <- setParameter(my_sim.base,"replicates",100)
my_sim.base  <- setParameter(my_sim.base,"patch_capacity",patch.capacity)
my_sim.base  <- setParameter(my_sim.base,"stat","{adlt.nbInd q.meanG_p}")
my_sim.base  <- setParameter(my_sim.base,"mating_nb_offspring_model",0)
my_sim.base  <- setParameter(my_sim.base,"fem_sex_allocation","Z1")
allele = data.frame("col_locus" = rep(1,255), "col_allele" = seq(1,255,1), "col_allelic_value" = seq(0,0.5,length.out = 255))
my_sim.base  <- addFile(my_sim.base,"quanti_allelic_file",allele)
my_sim.base  <- setParameter(my_sim.base,"quanti_loci",1)
my_sim.base  <- setParameter(my_sim.base,"quanti_mutation_rate",0.0001)
my_sim.base  <- setParameter(my_sim.base,"quanti_all",255)
my_sim.base  <- setParameter(my_sim.base,"patch_ini_size",patch.capacity)
```

```{r}
my_sim = my_sim.base
my_sim@sim.name <- "q"
run(my_sim,verbose = F)
```

##Result
### Extinction without any repopulation
#### Launching simulation

```{r}
stat <- loadStatRep(my_sim)
stat.rep <- stat$q.meanG[stat$replicate == 1]
n.rep = max(stat$replicate)
plot(stat.rep, type="l",ylim=c(0,1))
final.q <- rep(tail(stat.rep,1),n.rep)
for(i in 2:n.rep){
  stat.rep <- stat$q.meanG[stat$replicate == i]
  lines(stat.rep, type="l")
  final.q[i] <- tail(stat.rep,1)
}
hist(final.q,20)
```

### Same simulation but without the fem_sex_allocation

```{r}
my_sim.base = new("simulation",sim.dir = "female_sex_allocation/")
my_sim.base@sim.name <- "ntrl"
my_sim.base  <- setParameter(my_sim.base,"generations",n.iter)
my_sim.base  <- setParameter(my_sim.base,"replicates",100)
my_sim.base  <- setParameter(my_sim.base,"patch_capacity",patch.capacity)
my_sim.base  <- setParameter(my_sim.base,"stat","{adlt.nbInd q.meanG_p}")
my_sim.base  <- setParameter(my_sim.base,"mating_nb_offspring_model",0)
allele = data.frame("col_locus" = rep(1,255), "col_allele" = seq(1,255,1), "col_allelic_value" = seq(0,0.5,length.out = 255))
my_sim.base  <- addFile(my_sim.base,"quanti_allelic_file",allele)
my_sim.base  <- setParameter(my_sim.base,"quanti_loci",1)
my_sim.base  <- setParameter(my_sim.base,"quanti_mutation_rate",0.000001)
my_sim.base  <- setParameter(my_sim.base,"quanti_all",255)
my_sim.base  <- setParameter(my_sim.base,"patch_ini_size",patch.capacity)
```

```{r}
my_sim = my_sim.base
run(my_sim,verbose = F)
```


```{r}
my_sim = my_sim.base
stat = loadStatRep(my_sim)
stat.rep <- stat$q.meanG[stat$replicate == 1]
n.rep = max(stat$replicate)
plot(stat.rep, type="l",ylim=c(0,1))
final.ntrl <- rep(tail(stat.rep,1),n.rep)
for(i in 2:n.rep){
  stat.rep <- stat$q.meanG[stat$replicate == i]
  lines(stat.rep, type="l")
  final.ntrl[i] <- tail(stat.rep,1)
}
hist(final.ntrl,20)
```

```{r}
res = chisq.test(final.ntrl, final.q)
stopifnot(res$p.value <0.01)
```

