---
title: "Testing the fitness landscape on various patch"
output:
html_document: default
---

This notebook test if we can draw an arbitrary fitness landscape for defining how we translate phenotype value into fitness for various patch. 

We do this using by trying to draw an image using a heatmap of the phenotype. 

### In case it is not working, install some stupid package
```{r,eval = FALSE}
install.packages('gifski')
install.packages("png")
if (packageVersion('knitr') < '1.20.14') {
  remotes::install_github('yihui/knitr')
}
```

### Loading packages
```{r}
devtools::load_all(path="../rquantinemo")
library(png)
```
### Reading an input image
```{r}
Image <- readPNG("sam.png")
dim1 <-  dim(Image)[1]
dim2 <-  dim(Image)[2]
```

### Defining the fitness landscape    
We just take a landscape which follow a Gaussian (stabilizing selection) with the highest value given by the value of the pixel of the picture.
```{r}
phenotype_reduce <- seq(-1,1,0.01)
landscape = matrix(rep(0,dim1*dim2*201),ncol=201)
for (x in 1:dim1){
  for (y in 1:dim2){
      landscape[(x -1) * dim2 + y, ] <-  exp(-(1-2*Image[x,y] - phenotype_reduce)**2/1.5)
  }
}
phenotype = matrix(rep(0,dim1*dim2*201),ncol=201)
for (x in 1:dim1){
  for (y in 1:dim2){
          phenotype[(x -1) * dim2 + y, ] <-phenotype_reduce
  }
}
```


### Writting the phenotype landscape into file readable by Qn
```{r}
write_matrix_quanti <- function(input.matrix, file.name){
  write("{", file = file.name)
  for (i in 1:(nrow(input.matrix))){
    write("{", file = file.name,append=TRUE)
    write(paste(input.matrix[i,], " "), file = file.name,append=TRUE)
    write("}", file = file.name,append=TRUE)
  }
  write("}", file = file.name,append=TRUE)
}
sim.dir = "fitness_landscape_various_patch/"
dir.create(sim.dir)
write_matrix_quanti(t(landscape), paste(sim.dir, "/landscape.txt",sep=""))
write_matrix_quanti(t(phenotype), paste(sim.dir, "/phenotype.txt",sep=""))
```

### Setting the parameters for the simulation    

We are simulating a square of patch of dimension dim1 x dim2 (see image size). The selected phenotype depend on the picture uploaded.
For the first 30 generations, we have no migration. We then turn on migration for 20 generations. 

```{r}
nb.generation = 30
nb.loci = 100
parameters = list("generations" = nb.generation,
                  "patch_number" = dim1*dim2,
                  "patch_capacity" = 100,
                  "quanti_loci" = nb.loci,
                  "quanti_all" = 2,
                  "quanti_selection_model" = 3,
                  "quanti_save_phenotype" = 1,
                  "dispersal_model" = 3,
                  "dispersal_border_model" = 1,
                  "dispersal_lattice_dims" =paste(c("{",dim2, dim1,"}"),collapse = " "),
                  "dispersal_rate" = "(1 0, 20 0.9 )",
                  "quanti_fitness_landscape" =  "$landscape.txt",
                  "quanti_phenotype_landscape" = "$phenotype.txt"
)
my_sim.base = new("simulation",sim.dir = sim.dir, parameters = parameters)
```

### Creating and adding the allelic file
```{r}
allele_distrib = data.frame("col_locus" =  rep(seq(1,nb.loci,1),each = 2),
                          "col_allele" =  rep(c(1,2),nb.loci),
                          "col_allelic_value" = rep(c(0.005,-0.005),nb.loci), 
                          "col_ini_freq" =rep(0.5,2*nb.loci))
my_sim.base <-  addFile(my_sim.base, "quanti_allelic_file",allele_distrib)
```

### Running the simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "beautiful_picture"
run(my_sim, verbose = T)
```

### Analysing results   
We then load the phenotype and compute the mean phenotype per patch. By plotting a heatmap of the phenotype, we retrieve the initial image. Fantastic, no?
```{r, animation.hook='gifski'}
for (generation in 1:nb.generation){
  geno <- loadPheno(my_sim,generation = generation)
  geno_per_patch = matrix(geno[,2],nrow = 100)
  all_mean <- colMeans(geno_per_patch)
  squared.pheno <- matrix(all_mean, ncol = dim2, byrow = T)
  image(-t(squared.pheno[121:1,]), yaxt='n', xaxt='n',main = paste(c("generation: ",generation)), col = gray.colors(12), asp=1.21)
}
```

