---
title: "Testing the fitness landscape"
output:
html_document: default
---

This notebook test if we can draw an arbitrary fitness landscape for defining how we translate phenotype value into fitness. To do so, we introduce a two-picks landscape, and check that the mean fitness of the population converge, randomly, towards one of these two positions. 

### loading package and setting minimal simulation
```{r}
devtools::load_all("../RQuantiNemo")
```


```{r}
parameters = list("generations" = 1000,
                  "patch_capacity" = 1000,
                  "replicates" = 10,
                  "quanti_loci" = 1,
                  "quanti_all" = 255,
                  "quanti_allelic_var" = 4,
                  "quanti_selection_model" = 3,
                  "stat" = "{q.adlt.nbAll q.adlt.ho q.meanG_p }"
)
my_sim.base = new("simulation",sim.dir = "fitness_landscape/", parameters = parameters)
```


##Result
### Two picks landscape
#### Launching simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "two_pick"
quanti_fitness_landscape = "{0.00 0.05 0.72 0.72 0.05 0.00 0.05 0.72 0.72 0.05 0.00}"
quanti_phenotype_landscape = "{-4.0 -3.2 -2.1 -1.9 -0.8 0.0 0.8 1.9 2.1 3.2 4.0}"

my_sim <- setParameter(my_sim, "quanti_fitness_landscape", quanti_fitness_landscape)
my_sim <- setParameter(my_sim, "quanti_phenotype_landscape ", quanti_phenotype_landscape)
run(my_sim, verbose = F)
```

####result of a landscape with two bumps

We expect the final phenotype to be either close to 2 or close to -2 
```{r}
pfl <- as.numeric(unlist(strsplit(gsub("\\{|\\}","",quanti_fitness_landscape)," ")))
ppl <- as.numeric(unlist(strsplit(gsub("\\{|\\}","",quanti_phenotype_landscape)," ")))
plot(ppl, pfl, type = "b", main = "Fitness Landscape", xlab = "phenotype", ylab = "Fitness")

gen <- loadStatRep(my_sim)
res <- matrix(gen$q.meanG,ncol =10)
plot(res[,1],type="l",xlim = c(0,50),ylim = c(-4,4),xlab = "generation",ylab = "Mean Phenotype",main = "evolution of the phenotype")
for (i in 2:9) 
{
  lines(res[,i])
}
final.pheno = tail(res,1)

count.neg <- sum(final.pheno < 0)
count.pos <- sum(final.pheno > 0)
count.valid <- sum(abs(final.pheno) > 1.75 & abs(final.pheno < 2.25))
stopifnot(count.pos >1)
stopifnot(count.neg >1)
stopifnot(count.valid > 7) #allows for two values out of range
```