---
title: "Testing the fitness landscape on various patch"
output:
html_document: default
---

This notebook test if we can draw an arbitrary fitness landscape for defining how we translate phenotype value into fitness for various patch. 


### Loading packages
```{r}
devtools::load_all("../rquantinemo")
```

### Defining the fitness landscape    
We just take a landscape which follow a Gaussian (stabilizing selection) with the highest value given by the value of the pixel of the picture.
```{r}
dim1 <-  25
dim2 <-  25
phenotype_reduce <- seq(-1,1,0.01)
landscape = matrix(rep(0,dim1*dim2*201),ncol=201)
for (x in 1:dim1){
  for (y in 1:dim2){
      x_renorm = 2*(x - dim1/2)/dim1 #goes between -1 and 1
      y_renorm = 2*(y - dim2/2)/dim2
      fancy_shape <- 2*sqrt(x_renorm**2 + y_renorm**2)/sqrt(2)-1
      landscape[(x -1) * dim2 + y, ] <-  exp(-(fancy_shape - phenotype_reduce)**2/0.2)
  }
}
phenotype = matrix(rep(0,dim1*dim2*201),ncol=201)
for (x in 1:dim1){
  for (y in 1:dim2){
          phenotype[(x -1) * dim2 + y, ] <- phenotype_reduce
  }
}
plot(phenotype_reduce, landscape[(x -1) * dim2 + y, ])
```


### Writting the phenotype landscape into file readable by Qn
```{r}
write_matrix_quanti <- function(input.matrix, file.name){
  write("{", file = file.name)
  for (i in 1:(nrow(input.matrix))){
    write("{", file = file.name,append=TRUE)
    write(paste(input.matrix[i,], " "), file = file.name,append=TRUE)
    write("}", file = file.name,append=TRUE)
  }
  write("}", file = file.name,append=TRUE)
}
sim.dir = "fitness_landscape_various_patch_test/"
dir.create(sim.dir, showWarnings = FALSE)
write_matrix_quanti(t(landscape), paste(sim.dir, "/landscape.txt",sep=""))
write_matrix_quanti(t(phenotype), paste(sim.dir, "/phenotype.txt",sep=""))
```

### Setting the parameters for the simulation    

We are simulating a square of patch of dimension dim1 x dim2 (see image size). The selected phenotype depend on the picture uploaded.
For the first 30 generations, we have no migration. We then turn on migration for 20 generations. 

```{r}
nb.loci = 100
nb.generation = 50
nb.individual = 50
parameters = list("generations" = nb.generation,
                  "patch_number" = dim1*dim2,
                  "patch_capacity" = nb.individual,
                  "quanti_loci" = nb.loci,
                  "quanti_all" = 2,
                  "quanti_selection_model" = 3,
                  "quanti_save_phenotype" = 1,
                  "dispersal_model" = 3,
                  "dispersal_border_model" = 1,
                  "dispersal_lattice_dims" =paste(c("{",dim1, dim2,"}"),collapse = " "),
                  "dispersal_rate" = 0,
                  "quanti_fitness_landscape" =  "$landscape.txt",
                  "quanti_phenotype_landscape" = "$phenotype.txt"
)
my_sim.base = new("simulation",sim.dir = sim.dir, parameters = parameters)
```

### Creating and adding the allelic file
```{r}
allele_distrib = data.frame("col_locus" =  rep(seq(1,nb.loci,1),each = 2),
                          "col_allele" =  rep(c(1,2),nb.loci),
                          "col_allelic_value" = rep(c(0.005,-0.005),nb.loci), 
                          "col_ini_freq" =rep(0.5,2*nb.loci))
my_sim.base <-  addFile(my_sim.base, "quanti_allelic_file",allele_distrib)
```

### Running the simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "circle"
run(my_sim, verbose = F)
```

### Analysing results   
We then load the phenotype and compute the mean phenotype per patch. By plotting a heatmap of the phenotype, we retrieve the initial image. Fantastic, no?
```{r}
for (generation in c(1,2,5,10,nb.generation)){
  geno <- loadPheno(my_sim,generation = generation)
  geno_per_patch = matrix(geno[,2],nrow = nb.individual)
  all_mean <- colMeans(geno_per_patch)
  squared.pheno <- matrix(all_mean, ncol = dim2, byrow = T)
  image(-t(squared.pheno[dim1:1,]), yaxt='n', xaxt='n',main = paste(c("generation: ",generation)), col = gray.colors(12), asp=1.21)
}
```


### Formal test
We then load the phenotype and compute the mean phenotype per patch. By plotting a heatmap of the phenotype, we retrieve the initial image. Fantastic, no?
```{r}

  geno <- loadPheno(my_sim,generation = -1)
  geno_per_patch = matrix(geno[,2],nrow = nb.individual)
  all_mean <- colMeans(geno_per_patch)
  all_dist = c()
for (x in 1:dim1){
  for (y in 1:dim2){
      x_renorm = 2*(x - dim1/2)/dim1 #goes between -1 and 1
      y_renorm = 2*(y - dim2/2)/dim2
      fancy_shape <- 2*sqrt(x_renorm**2 + y_renorm**2)/sqrt(2)-1
      all_dist = c(all_dist, fancy_shape-all_mean[(x -1) * dim2 + y] )
  }
}
  stopifnot(sum(all_dist*all_dist)< 6)
```
