---
title: "Test of the friction factor"
output:
  html_document: default
---
The goal of this notebook is to check if the friction factor is working well.
To do so, we consider a island model, and we set a friction coefficient to some iceland. 
If we have a friction larger than one, the number of individuals on this island shoud decrease. 
If it's superior to one, it should increase. This can be compared to analytical results. 

### loading package and setting minimal simulation
```{r}
devtools::load_all(pkg="../RQuantiNemo")
parameters = list("generations" = 100,
                  "patch_capacity" = 100,
                  "patch_number" = 20,                  
                  "mating_nb_offspring_model" = 1,
                  "dispersal_model" = 0,
                  "dispersal_rate" = 0.1,
                  "replicates" = 25,
                  "stat" = "{adlt.nbInd_p}")
my_sim.base = new("simulation",sim.dir = "friction/", parameters = parameters)
```



## Result 
### No dispersal factor
#### Launching simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "no_friction"
success <- run(my_sim, verbose = FALSE)
```
#### Ploting result
```{r}
stat <- loadStat(my_sim)
plot(stat$adlt.nbInd_p01, main = "Evolution of the number of individual", ylab = "Nb of individual", xlab = "generations", ylim = c(90,110), type = "l")
for (patch in 1:20) {
  var = paste("adlt.nbInd_p",formatC(patch, width = 2,  flag = "0"),sep="")
  lines(stat[[var]])  
}
```

### All dispersal factor set to 1
#### Launching simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "1_friction"
my_sim <- setParameter(my_sim, "patch_friction", "{rep(1,12)}")
success <- run(my_sim, verbose = FALSE)
```
#### Ploting result
```{r}
stat <- loadStat(my_sim)
plot(stat$adlt.nbInd_p01, main = "Evolution of the number of individual", ylab = "Nb of individual", xlab = "generations", ylim = c(90,110), type = "l")
for (patch in 1:20) {
  var = paste("adlt.nbInd_p",formatC(patch, width = 2,  flag = "0"),sep="")
  lines(stat[[var]])  
}
```


### two dispersal factor set to 0.
#### Launching simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "0_friction"
my_sim <- setParameter(my_sim, "patch_friction", "{0 0 rep(1,10)}")
success <- run(my_sim, verbose = FALSE)
```
#### Ploting result
```{r}
stat <- loadStat(my_sim)
plot(stat$adlt.nbInd_p01, main = "Evolution of the number of individual", ylab = "Nb of individual", xlab = "generations", ylim = c(90,110), type = "l")
for (patch in 1:20) {
  var = paste("adlt.nbInd_p",formatC(patch, width = 2,  flag = "0"),sep="")
  lines(stat[[var]])  
}
stopifnot(tail(stat$adlt.nbInd_p01) > 200)
```




### two dispersal factor set to 2.
#### Launching simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "2_friction"
my_sim <- setParameter(my_sim, "patch_friction", "{2 2 rep(1,10)}")
success <- run(my_sim, verbose = FALSE)
```
#### Ploting result
```{r}
stat <- loadStat(my_sim)
plot(stat$adlt.nbInd_p01, main = "Evolution of the number of individual", ylab = "Nb of individual", xlab = "generations", ylim = c(90,110), type = "l")
for (patch in 1:20) {
  var = paste("adlt.nbInd_p",formatC(patch, width = 2,  flag = "0"),sep="")
  lines(stat[[var]])  
}
stopifnot(tail(stat$adlt.nbInd_p01) == 0 )
```