---
title: "Testing various distribution for initial genotype"
output:
  html_document: default
---
In this notebook, we check if the value of the genotype can be set monommorphically or polymorphaly, and we check the corresponding phenotype distribution


###loading package and setting minimal simulation
```{r}
devtools::load_all(pkg="../RQuantiNemo")
parameters = list("generations" = 250,
                  "patch_capacity" = 10000,
                  "quanti_loci" = 1,
                  "quanti_save_phenotype" = 1,
                  "quanti_mutation_rate" = 0.01
                  )
my_sim.base = new("simulation",sim.dir = "initial_genotype/", parameters = parameters)
```

## Result
### Monomorph initial genotype
#### Launching simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name = "monomorph"
my_sim <- setParameter(my_sim,"quanti_ini_allele_model",1)
success <- run(my_sim, verbose = F)
```

#### Plotting and checking result
```{r}
res <- loadPheno(my_sim, generation = 1)
stopifnot(all(res$V2==0))
res <- loadPheno(my_sim, generation = 2)
hist(res$V2)
res <- loadPheno(my_sim, generation = -1)
hist(res$V2)
```
### Polymorph initial genotype
#### Launching simulation
```{r}
my_sim = my_sim.base
my_sim@sim.name = "polymorph"
my_sim <- setParameter(my_sim,"quanti_ini_allele_model",0)
my_sim <- setParameter(my_sim,"quanti_allelic_var",2)
success <- run(my_sim, verbose = F)
```

#### Plotting and checking result
```{r}
res <- loadPheno(my_sim, generation = 1)
hist(res$V2, freq = FALSE)
b=seq(-10,10,0.1)
lines(b,dnorm(b,0,(2)),col="red")
var(res$V2)
stopifnot(var(res$V2)<4.15)
stopifnot(var(res$V2)>3.85)
res <- loadPheno(my_sim, generation = -1)
hist(res$V2)
```

