---
title: "Using seed"
output:
  html_document: default
---

##Introduction
The goal of this notebook is to see if seeds are working. First we check that two simulations with the same seed leads to the same result, and two simulation with different seed leads to different result.
Then we check if we can reload the seed from a previous simulation. 

### Setting general parameter for the simulaiton
```{r}
devtools::load_all("../RQuantiNemo")
parameters = list(
  "generations" = 100,
  "mating_nb_offspring_model"=2, #randomness come from here
  "patch_capacity" = 100,
  "mean_fecundity" = 1,
  "replicates" = 2,
  "stat" = "{adlt.nbInd}"
)
my_sim.base <- new("simulation", sim.dir = "loading_seed/",parameters = parameters)
```

## Checking for defined by user seed   
Simulation 1 and 2 have common seeds while simulation 3 has different seed 
```{r}
my_sim1 <- my_sim.base
my_sim2 <- my_sim.base
my_sim3 <- my_sim.base
my_sim1@sim.name = "seed1"
my_sim2@sim.name = "seed2"
my_sim3@sim.name = "seed3"
my_sim1 <- setParameter(my_sim1,"seed","1234")
my_sim2 <- setParameter(my_sim2,"seed","1234")
my_sim3 <- setParameter(my_sim3,"seed","1235")
success <- run(my_sim1, verbose = F)
success <- run(my_sim2, verbose = F)
success <- run(my_sim3, verbose = F)
```

#### Ploting the result and checking them
```{r}
stat1 = loadStat(my_sim1)
stat2 = loadStat(my_sim2)
stat3 = loadStat(my_sim3)
plot(stat1$adlt.nbInd, type = "l")
points(stat2$adlt.nbInd)
points(stat3$adlt.nbInd)
stopifnot(all(stat1$adlt.nbInd == stat2$adlt.nbInd))
stopifnot(!all(stat1$adlt.nbInd == stat3$adlt.nbInd))
```

### Automatic seed    
#### Launching simulation
Now, we have no defined seed, but we take the one of the output file to set it in an input file, and check that we have the same result. 
```{r}
my_sim4 <- my_sim.base
my_sim4@sim.name = "seed4"
sucess <- run(my_sim4, verbose = F)
seeds <- readLines("loading_seed/seed4/simulation.log")[[grep('seed ',readLines("loading_seed/seed4/simulation.log"))]]
seeds <- substr(seeds,6,nchar(seeds))
my_sim5 <- my_sim.base
my_sim5@sim.name = "seed5"
my_sim5 <- setParameter(my_sim5,"seed",seeds)
sucess <- run(my_sim5, verbose = F)
```

#### Plotting and checking result. 
```{r}
stat4 = loadStat(my_sim4)
stat5 = loadStat(my_sim5)
plot(stat4$adlt.nbInd, type = "l")
points(stat5$adlt.nbInd)
stopifnot(all(stat1$adlt.nbInd == stat2$adlt.nbInd))
```