---
title: "Test the different input macro"
output:
  html_document: default
---
The goal of this notebook is to check how does the macros perform

### loading package and setting minimal simulation
```{r}
devtools::load_all(pkg="../RQuantiNemo")
parameters = list("generations" = 5,
                  "patch_capacity" = 100,
                  "patch_number" = 1000,
                  "stat" = "{adlt.nbInd_p}")
my_sim.base = new("simulation",sim.dir = "macro/", parameters = parameters)
```

##Result
### seq
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "seq"
my_sim <- setParameter(my_sim, "patch_ini_size", "{seq(1,1000,1000)}")
run(my_sim, verbose =FALSE)
```
####Checking resut
```{r}
stat <- loadStatPatch(my_sim, "adlt.nbInd_p")
stopifnot(stat[1, ]==seq(1,1000,length.out = 1000))
```

### rep
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "rep"
my_sim <- setParameter(my_sim, "patch_ini_size", "{rep(5,1000)}")
success <- run(my_sim, verbose =FALSE)
```
####Checking resut
```{r}
stat <- loadStatPatch(my_sim, "adlt.nbInd_p")
stopifnot(stat[1, ]==rep(5,1000))
```


### rnorm
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "runif"
my_sim <- setParameter(my_sim, "patch_ini_size", "{rnorm(1000,25,5)}")
success <- run(my_sim, verbose =F)
```
####Checking resut
```{r}
stat <- loadStatPatch(my_sim, "adlt.nbInd_p")
hist(stat[1, ],20)
print(" ")
hist(round(rnorm(1000,25,5),20))

res <- ks.test(stat[1, ], round(rnorm(1000,25,5)))
stopifnot(res$p.value>0.01)
```

### runif
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "runif"
my_sim <- setParameter(my_sim, "patch_ini_size", "{runif(1000,10,20)}")
success <- run(my_sim, verbose =F)
```
####Checking resut
```{r}
stat <- loadStatPatch(my_sim, "adlt.nbInd_p")
hist(stat[1, ])
print(" ")
hist(floor(runif(1000,10,20)))
table(stat[1, ])
res <- ks.test(stat[1, ], floor(runif(1000,10,20)))
stopifnot(res$p.value>0.01)
```

### rlnorm
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "rlnorm"
my_sim <- setParameter(my_sim, "patch_ini_size", "{rlnorm(1000,3,1)}")
success <- run(my_sim, verbose = F)
```
####Checking resut
```{r}
stat <- loadStatPatch(my_sim, "adlt.nbInd_p")
hist(log(stat[1, ]))
print(" ")
hist(log(ceiling(rlnorm(1000,3,1))))
res <- ks.test(stat[1, ], log(ceiling(rlnorm(1000,3,1))))
```
### RGamma
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "rgamma"
my_sim <- setParameter(my_sim, "patch_ini_size", "{rgamma(1000,3,1)}")
success <- run(my_sim, verbose =F)
```
####Checking resut
```{r}
stat <- loadStatPatch(my_sim, "adlt.nbInd_p")
hist(stat[1, ])
print(" ")
hist(floor(rgamma(1000,3,1)))
res <- ks.test(stat[1, ], floor(rgamma(1000,3,1)))
stopifnot(res$p.value>0.01)
```

### rbeta
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "rbeta"
my_sim <- setParameter(my_sim, "patch_ini_size", "{rbeta(1000,2,1,0,100)}")
success <- run(my_sim, verbose =F)
```
####Checking resut
```{r}
stat <- loadStatPatch(my_sim, "adlt.nbInd_p")
hist(stat[1, ])
print(" ")
hist(round(100*rbeta(1000,2,1)))
res <- ks.test(stat[1, ], round(100*rbeta(1000,2,1)))
stopifnot(res$p.value>0.01)
```


### rpois
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "rpois"
my_sim <- setParameter(my_sim, "patch_ini_size", "{rpois(1000,10)}")
success <- run(my_sim, verbose =F)
```
####Checking resut
```{r}
stat <- loadStatPatch(my_sim, "adlt.nbInd_p")
hist(stat[1, ])
print(" ")
hist(rpois(1000,10))
res <- ks.test(stat[1, ], rpois(1000,10))
stopifnot(res$p.value>0.01)
```

### sample
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "sample"
my_sim <- setParameter(my_sim, "patch_ini_size", "{rsample(1000,1,8,10,14,20)}")
success <- run(my_sim, verbose =F)
```
####Checking resut
```{r}
stat <- loadStatPatch(my_sim, "adlt.nbInd_p")
hist(stat[1, ])
print(" ")
hist(sample(c(8,10,14,20),1000,rep = T))
res <- ks.test(stat[1, ],sample(c(8,10,14,20),1000,rep = T))
stopifnot(res$p.value>0.01)
```