---
title: "testing population grow"
output:
  html_document: default
---
In this notebook, we show the different possible population grow that are implemented in Quantinemo, and compare them to R version to see if we observe the expected behaviour. 


##loading package and setting minimal simulation
```{r}
devtools::load_all("../RQuantiNemo")
my_sim.base = new("simulation",sim.dir = "population_grow/",parameters=list("generations" = 1000, "patch_capacity" = 1000,"stat" = "{adlt.nbInd}"))
```

# Population is equal to patch capacity. 
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "constant"
my_sim <- setParameter(my_sim,"mating_nb_offspring_model",0)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd
# Displaying result
plot(res,xlab = "generation",ylab = "Population size",main = "Evolution of the population size",log="y",type = "l",col="red")
lines(rep(1000,1000),col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
# Test
stopifnot(tail(stats$adlt.nbInd,1)==1000)
```
# Population remain constant 
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "patch_capacity"
my_sim <- setParameter(my_sim,"mating_nb_offspring_model",1)
my_sim <- setParameter(my_sim,"patch_ini_size",500)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd
# Displaying result
plot(res,xlab = "generation",ylab = "Population size",main = "Evolution of the population size",log="y",type = "l",col="red")
lines(rep(500,1000),col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
# Test
stopifnot(tail(stats$adlt.nbInd,1)==500)
```

#  Poisson(N*fertility)  

 we compare to a (here computed) equivalent simulation. 
 Warning that the population might go extinct... rerun it to have more similar resutl. 
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "Poisson"
grow.rate = 1.1
ini.size = 20
generations = 100
my_sim <- setParameter(my_sim,"mating_nb_offspring_model",2)
my_sim <- setParameter(my_sim,"generations",generations)
my_sim <- setParameter(my_sim,"patch_ini_size",ini.size)
my_sim <- setParameter(my_sim,"mean_fecundity",grow.rate)
my_sim <- setParameter(my_sim,"seed",150)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd
pop <-  numeric(length=generations)
pop[1]=ini.size
set.seed(123)
for (i in 2:generations)
{
  pop[i] <-  rpois(1,pop[i-1]*grow.rate)
}
plot(res,xlim = c(0,generations),ylim = c(5,10*grow.rate^generations),xlab = "generation",ylab = "Population size",main = "Evolution of the population size",log="y",type = "l",col="red")
lines(pop,col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
pop.sim <- tail(stats$adlt.nbInd,1)
pop.exp <- tail(pop,1)
diff <- pop.sim/pop.exp
print(abs(log(pop.sim)-log(pop.exp)))
stopifnot(abs(log(pop.sim)-log(pop.exp))<0.6)
```

# Round(N*fertility)  

Depending on the initialpopulation size, the population grow or stay constant
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "smooth_fertility"
grow.rate = 1.051
ini.size = 9
generations = 100
my_sim <- setParameter(my_sim,"mating_nb_offspring_model",3)
my_sim <- setParameter(my_sim,"generations",generations)
my_sim <- setParameter(my_sim,"patch_ini_size",ini.size)
my_sim <- setParameter(my_sim,"mean_fecundity",grow.rate)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd
pop <-  numeric(length=generations)
pop[1]=ini.size
for (i in 2:generations)
{
  pop[i] <-  round(pop[i-1]*grow.rate)
}
plot(res,xlim = c(0,generations),ylim = c(5,10*grow.rate^generations),xlab = "generation",ylab = "Population size",main = "Evolution of the population size",log="y",type = "l",col="red")
lines(pop,col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
pop.sim <- tail(stats$adlt.nbInd,1)
pop.exp <- tail(pop,1)
stopifnot(pop.sim == pop.exp)

#With a higer ini size
ini.size = 15
my_sim <- setParameter(my_sim,"patch_ini_size",ini.size)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd
pop <-  numeric(length=generations)
pop[1]=ini.size
for (i in 2:generations)
{
  pop[i] <-  round(pop[i-1]*grow.rate)
}
plot(res,xlim = c(0,generations),ylim = c(5,10*grow.rate^generations),xlab = "generation",ylab = "Population size",main = "Evolution of the population size",log="y",type = "l",col="red")
lines(pop,col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
pop.sim <- tail(stats$adlt.nbInd,1)
pop.exp <- tail(pop,1)
stopifnot(pop.sim == pop.exp)
```

# Round(N*fertility) + binomial(N*fertility)  

This type of grow is usefull if we want a faster way to compute the number of offspring, but that because of rounding, the smooth way does not start growing. 
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "smooth_fertility_corrected"
grow.rate = 1.02
ini.size = 10
generations = 100
my_sim <- setParameter(my_sim,"mating_nb_offspring_model",4)
my_sim <- setParameter(my_sim,"generations",generations)
my_sim <- setParameter(my_sim,"patch_ini_size",ini.size)
my_sim <- setParameter(my_sim,"mean_fecundity",grow.rate)
my_sim <- setParameter(my_sim,"seed",126)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd
pop <-  numeric(length=generations)
pop[1]=ini.size
set.seed(123)
for (i in 2:generations)
{
  pop[i] <-  floor(grow.rate*pop[i-1]) + rbinom(1,1,(pop[i-1]*grow.rate - as.integer(pop[i-1]*grow.rate)))
}
plot(res,xlim = c(0,generations),ylim = c(5,10*grow.rate^generations),xlab = "generation",ylab = "Population size",main = "Evolution of the population size",log="y",type = "l",col="red")
lines(pop,col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
pop.sim <- tail(stats$adlt.nbInd,1)
pop.exp <- tail(pop,1)
diff <- pop.sim/pop.exp
stopifnot(abs(log(pop.sim)-log(pop.exp))<0.1)
```

# Poisson(N*fertility) with a cut at patch_capacity
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "poisson_cut"
grow.rate = 1.05
ini.size = 20
generations = 200
my_sim <- setParameter(my_sim,"mating_nb_offspring_model",5)
my_sim <- setParameter(my_sim,"generations",generations)
my_sim <- setParameter(my_sim,"patch_ini_size",ini.size)
my_sim <- setParameter(my_sim,"mean_fecundity",grow.rate)
my_sim <- setParameter(my_sim,"seed",123)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd
pop <-  numeric(length=generations)
pop[1]=ini.size
set.seed(124)
for (i in 2:generations)
{
  pop[i] <-  rpois(1,pop[i-1]*grow.rate)
  pop[pop>1000] = 1000
}

plot(res,xlim = c(0,generations),ylim = c(5,10*grow.rate^generations),xlab = "generation",ylab = "Population size",main = "Evolution of the population size",log="y",type = "l",col="red")
lines(pop,col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
pop.sim <- tail(stats$adlt.nbInd,1)
pop.exp <- tail(pop,1)
stopifnot(pop.sim == pop.exp)
```

#(N*fertility) with a cut at patch_capacity
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "smooth_fertility_cut"
grow.rate = 1.05
ini.size = 20
generations = 200
my_sim <- setParameter(my_sim,"generations",generations)
my_sim <- setParameter(my_sim,"patch_ini_size",ini.size)
my_sim <- setParameter(my_sim,"mean_fecundity",grow.rate)
ini.size = 15
my_sim <- setParameter(my_sim,"mating_nb_offspring_model",6)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd
pop <-  numeric(length=generations)
pop[1]=ini.size
for (i in 2:generations)
{
  pop[i] <-  round(pop[i-1]*grow.rate)
}
pop[pop>1000] = 1000
plot(res,xlim = c(0,generations),ylim = c(5,10*grow.rate^generations),xlab = "generation",ylab = "Population size",main = "Evolution of the population size",log="y",type = "l",col="red")
lines(pop,col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
pop.sim <- tail(stats$adlt.nbInd,1)
pop.exp <- tail(pop,1)
stopifnot(pop.sim == pop.exp)
```

# (N*fertility) + binomial and cut
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "smooth_fertility_corrected_cut"
grow.rate = 1.05
ini.size = 10
generations = 200
my_sim <- setParameter(my_sim,"mating_nb_offspring_model",7)
my_sim <- setParameter(my_sim,"generations",generations)
my_sim <- setParameter(my_sim,"patch_ini_size",ini.size)
my_sim <- setParameter(my_sim,"mean_fecundity",grow.rate)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd
pop <-  numeric(length=generations)
pop[1]=ini.size
for (i in 2:generations)
{
  pop[i] <-  floor(grow.rate*pop[i-1]) + rbinom(1,1,(pop[i-1]*grow.rate - as.integer(pop[i-1]*grow.rate)))
}
pop[pop>1000] = 1000
plot(res,xlim = c(0,generations),ylim = c(5,10*grow.rate^generations),xlab = "generation",ylab = "Population size",main = "Evolution of the population size",log="y",type = "l",col="red")
lines(pop,col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
pop.sim <- tail(stats$adlt.nbInd,1)
pop.exp <- tail(pop,1)
diff <- pop.sim/pop.exp
stopifnot(diff < grow.rate^20,diff > grow.rate^(-20))
```
# Logistic grow
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "logistic"
r = 0.5
ini.size = 2
generations = 100
my_sim <- setParameter(my_sim,"mating_nb_offspring_model",8)
my_sim <- setParameter(my_sim,"generations",generations)
my_sim <- setParameter(my_sim,"patch_ini_size",ini.size)
my_sim <- setParameter(my_sim,"growth_rate",r)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd

f <- function(N,K,r){round((N*K*(1+r))/((N*(1+r))-N+K))}

plot(res,type="l",xlim = c(0,generations),ylim=c(0,1000),xlab = "generation",ylab = "Population size",main = "Evolution of the population size",col="red")

pop = seq(1:generations)
pop[1] <- ini.size
for (i in 2:generations){pop[i] <- f(pop[i-1],1000,r)}
lines(pop,col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
stopifnot(pop[10] ==res[10],pop[100] ==res[100] )
```


# Poisson(logistic grow)
```{r}
my_sim = my_sim.base
my_sim@sim.name <- "logistic_poisson"
r = 0.5
ini.size = 2
generations = 100
my_sim <- setParameter(my_sim,"mating_nb_offspring_model",9)
my_sim <- setParameter(my_sim,"generations",generations)
my_sim <- setParameter(my_sim,"patch_ini_size",ini.size)
my_sim <- setParameter(my_sim,"growth_rate",r)
my_sim <- setParameter(my_sim,"seed",100)
output <- run(my_sim, verbose = FALSE)
stats<- loadStat(my_sim)
res <- stats$adlt.nbInd

f <- function(N,K,r){round((N*K*(1+r))/((N*(1+r))-N+K))}

plot(res,type="l",xlim = c(0,generations),ylim=c(0,1000),xlab = "generation",ylab = "Population size",main = "Evolution of the population size",col="red")

pop = seq(1:generations)
pop[1] <- ini.size
set.seed(100)
for (i in 2:generations){pop[i] <- rpois(1,f(pop[i-1],1000,r))}
lines(pop,col="blue")
legend("topleft",legend = c("Expected","QuantiNemo"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) # gives the legend lines the correct color and width
stopifnot(tail(pop,1)-tail(res,1)<75)
```

