---
title: "Test random per replicate"
output:
  html_document: default
---
The goal of this notebook is to check if random per replicate work. Random per replicate allow to set wheter the Marco are interpreted once and for all replicate, or differently for each replicate.   
To do so, we run a simulation with two replicates, and a random initial population. If random_per_replicate = 0, we expect both simulation to have the same number of individuals at the beggining of the simulation. On the contrary, if random_per_replicate = 1, the initial population should have different sizes. 

### loading package and setting minimal simulation
```{r}
devtools::load_all("../RQuantiNemo")
parameters = list("generations" = 5,
                  "patch_capacity" = "100",
                  "replicates" = 2,
                  "logfile_type" = 1,
                  "patch_number" = 50,
                  "patch_ini_size", "{rnorm(50,25,5)}",
                  "stat" = "{adlt.nbInd_p}")
my_sim.base = new("simulation",sim.dir = "random_per_replicate/", parameters = parameters)
```

##Result
### random per replicate = 0
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "random0"
my_sim <- setParameter(my_sim, "random_per_replicate", 0)
my_sim <- setParameter(my_sim, "patch_ini_size", "{rnorm(50,25,5)}")
success <- run(my_sim, verbose =F)
```
####Checking resut
```{r}
stat <- loadStatRep(my_sim)
pop1 <- stat[stat$replicate==1 & stat$generation==1, 3:52]
pop2 <- stat[stat$replicate==2 & stat$generation==1, 3:52 ]
stopifnot(pop1==pop2)
```

### random per replicate = 1
#### Launching simulation
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "random1"
my_sim <- setParameter(my_sim, "patch_ini_size", "{rnorm(50,25,5)}")
my_sim <- setParameter(my_sim, "random_per_replicate", 1)
success <- run(my_sim, verbose =F)
```
####Checking resut
```{r}
stat <- loadStatRep(my_sim)
pop1 <- stat[stat$replicate==1 & stat$generation==1, 3:52]
pop2 <- stat[stat$replicate==2 & stat$generation==1, 3:52]
stopifnot(sum(pop1!=pop2)>0) #Some population might have the same size, but not all of them, so the sum should be much larger than 0. 
```