---
title: "Does the different type of selection work?"
output:
  html_document: default
---

the goal of this notebook is to check whether the different type of selection (soft/metapop/hard) are working correctly. To do so, we compare the speed of selection of some trait, and check wether they are selected or not.   
In the second part, we also check intermediate regime, which at the moment doesn't seem to work well. 


## loading package and setting minimal simulation
```{r}
devtools::load_all(pkg="../RQuantiNemo")
```

#### creating initial genotype
```{r}
getGenotype <- function(freq,pop){
  n1 = freq*pop
  n2 = pop-n1
  return(data.frame(col_1 = rep(c(1,2),c(n1,n2)),col_2 = c(rep(11,n1),rep(22,n2))))
}
```

#### setting general (common) parameters
we set two patch with 100 individuals. We have one trait, one locus and two allele, with value 0 and 1. First patch has only 0 and second patch has only 1, which mean that the phenotype of first population is 0 and of second population is 2. 
the optimal is at 0.5, which mean that pop 1 is better than pop 2 but not perfect. 
```{r}
my_sim <- new("simulation" ,sim.dir = "selection_level/")

#general pop
my_sim  <- setParameter(my_sim,"replicates",100)
my_sim  <- setParameter(my_sim,"generations",250)
my_sim  <- setParameter(my_sim,"patch_capacity",50)
my_sim  <- setParameter(my_sim,"patch_number",2)

#Mating system
my_sim  <- setParameter(my_sim,"mating_nb_offspring_model",8)
my_sim  <- setParameter(my_sim,"growth_rate",1.)

#loci
my_sim  <- setParameter(my_sim,"quanti_loci",1)
my_sim  <- setParameter(my_sim,"quanti_all",2)
my_sim  <- setParameter(my_sim,"selection_pressure_definition",0) #We define selection at patch level
my_sim  <- setParameter(my_sim,"dispersal_rate",0.) 
alleles <- data.frame(col_locus = c(1,1),col_allele = c(1,2),col_allelic_value = c(0, 1))
my_sim <-  addFile(my_sim, "quanti_allelic_file",alleles)
genotype <- getGenotype(0.5, my_sim@parameters[["patch_number"]]*20) #we fix 20 individual per patch here!
my_sim <-  addFile(my_sim, "quanti_ini_genotypes",genotype )

#selection
my_sim  <- setParameter(my_sim,"patch_stab_sel_intensity",2)
my_sim  <- setParameter(my_sim,"patch_stab_sel_optima",0.5)
my_sim  <- setParameter(my_sim,"quanti_selection_model",1)

#statistique
my_sim  <- setParameter(my_sim,"stat","{adlt.nbInd_p q.adlt.ho q.meanG_p }")
```

##testing for various level

###Soft selection
####Launching simulation
```{r}
my_sim@sim.name <- "soft_selection"
my_sim  <- setParameter(my_sim,"selection_level",0)
result <- run(my_sim, verbose=F)
```

```{r}
statSoft <- loadStat(my_sim)
plot(statSoft$adlt.nbInd_p1, main = "evolution of population size ", xlab = "generation", ylab = "nb. Individual", type = "l", col = "red", ylim = c(0,55))
legend("topleft",legend = c("patch 1","patch 2"),
lty=c(1,1),
lwd=c(2.5,2.5),
col=c("blue","red")) 
lines(statSoft$adlt.nbInd_p2, col = "blue")
stopifnot(tail(statSoft$adlt.nbInd_p1,1)==49)
stopifnot(tail(statSoft$adlt.nbInd_p2,1)==49)
```




##Metapop selection
```{r}
my_sim@sim.name <- "metapop_selection"
my_sim  <- setParameter(my_sim,"selection_level",1)
result <- run(my_sim,verbose=F)
```

```{r}
statMetaPop <- loadStat(my_sim)
plot(statMetaPop$adlt.nbInd_p1, main = "evolution of population size ", xlab = "generation", ylab = "nb. Individual", type = "l", col = "red", ylim = c(0,100))
legend("topleft",legend = c("patch 1","patch 2"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) 
lines(statMetaPop$adlt.nbInd_p2, col = "blue")
stopifnot(tail(statMetaPop$adlt.nbInd_p1,1)==99)
stopifnot(tail(statMetaPop$adlt.nbInd_p2,1)==0)
```
##Hard selection
```{r}
my_sim@sim.name <- "hard_selection"
my_sim  <- setParameter(my_sim,"selection_level",2)
writeInput(my_sim)
result <- run(my_sim,verbose=F)
```

```{r}
statHard <- loadStat(my_sim)
plot(statHard$adlt.nbInd_p1, main = "evolution of population size ", xlab = "generation", ylab = "nb. Individual", type = "l", col = "red", ylim = c(0,100))
legend("topleft",legend = c("patch 1","patch 2"),
lty=c(1,1), # gives the legend appropriate symbols (lines)
lwd=c(2.5,2.5),
col=c("blue","red")) 
lines(statHard$adlt.nbInd_p2, col = "blue")
stopifnot(tail(statHard$adlt.nbInd_p1,1)==45)
stopifnot(tail(statHard$adlt.nbInd_p2,1)==24)
```
