---
title: "Test if we can perform statistic on only a sub group of patch/individual"
output:
  html_document: default
---
The goal of this notebook is to check if the parameters  to constrain the considered populations and/or individuals taken into account for statistic work.   
In the first part, we try to select subpatch. To do so we simply specify that we want the statistics of subpatch, and check in the output file that the statistics are only given for these subpatches (for stat computed for each patch).

### loading package and setting minimal simulation
```{r}
devtools::load_all(pkg="../RQuantiNemo")
parameters = list("generations" = 3,
                  "dispersal_rate" = 0.2,
                  "mating_nb_offspring_model" =6,
                  "mating_system" =3,
                  "patch_capacity" = 100,
                  "growth_rate" = 0.1,
                  "patch_number" = 9,
                  "stat" = "{adlt.nbInd_p adlt.nbFem_p adlt.nbMal_p adlt.nbInd adlt.meanInd adlt.sexRatio}")
my_sim.base = new("simulation",sim.dir = "stat_sampling/", parameters = parameters)
```

##Result
### Sampling only over half the patch (randomly choosen)
#### Launching simulation and testing resutl
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "s_patch"
my_sim <- setParameter(my_sim, "sampled_patches", "5")
all.sample = c()
all.sample.th = c()
for(i in 1:100){
  success <- run(my_sim, verbose = FALSE)
  stat <- loadStat(my_sim)
  stat.names <- names(stat)
  patch.names <- stat.names[grepl("adlt.nbInd_p",stat.names)]
  patch.number <- as.numeric(substr(patch.names,13,13))
  all.sample <- c(all.sample,patch.number)
  all.sample.th <- c(all.sample.th,sample(seq(1,9,1),5))
}
res <- ks.test(all.sample.th, all.sample)
res$p.value
stopifnot(res$p.value > 0.01)
```

### Sampling only over a definite set of patch
#### Launching simulation and testing result
```{r}
my_sim <- my_sim.base
my_sim@sim.name <- "s_patch"
my_sim <- setParameter(my_sim, "sampled_patches", "{1 3 5 7 8}")
success <- run(my_sim, verbose = FALSE)
stat <- loadStat(my_sim)
stat.names <- names(stat)
patch.names <- stat.names[grepl("adlt.nbInd_p",stat.names)]
patch.number <- as.numeric(substr(patch.names,13,13))
stopifnot(patch.number == c(1, 3, 5, 7, 8))
```


### Sampling within the population of a patch
#### Launching simulation and testing result
To check the statistics, we need something a bit more evolved, so we had one quantitative trait. We then compare the value that give us the statistics for the genotype wheter we consider the entire population or only a sub-samble. The variance for this various case should be different. 
```{r}
parameters = list("generations" = 1, 
                  "patch_capacity" = 1000,
                  "quanti_loci" = 1,
                  "quanti_allelic_var" = 1,
                  "quanti_save_phenotype" = 1,
                  "quanti_all" = 51,
                  "quanti_output" = 1,
                  "stat" = "{q.meanG_p }"
)
my_sim.base@parameters = parameters
my_sim <- my_sim.base
my_sim@sim.name <- "s_var2"
success <- run(my_sim, verbose = F)
phenotype.QN <- loadPheno(my_sim)
nb.rep = 1000
```

```{r}
all.value <- read.table("stat_sampling/s_var2/allelic_values.txt", skip = 16)
plot(all.value$V3,cumsum(all.value$V4), t = "p")
print(" ")
all.value2 <- read.table("stat_sampling/s_var1/allelic_values.txt", skip = 16)
lines(all.value2$V3,cumsum(all.value2$V4))
lines(seq(-6,6,0.01), pnorm(seq(-6,6,0.01),0,1), col = "red")
sum(all.value$V4)
sum(all.value2$V4)
```

```{r}
genotype.r <- rnorm(nb.rep*2,0,1)
phenotype.r <- genotype.r[1:1000] + genotype.r[1001:2000]
hist(phenotype.r)
```

####Single individual
```{r}
phenotype.1s = c()
for (i in 1:nb.rep){
  my_sim <- my_sim.base
  my_sim <- setParameter(my_sim, "patch_sample_size", 1)
  my_sim@sim.name <- "s_individual"
  success <- run(my_sim, verbose = F)
  stat.ind <- loadStat(my_sim)
  phenotype.1s <- c(phenotype.1s, (stat.ind$q.meanG))
}
loadPheno(my_sim)
sd(phenotype.1s)
```

```{r}
all.value2 <- read.table("stat_sampling/s_var2/allelic_values.txt", skip = 16)
plot(all.value2$V3,all.value2$V4)
print(" ")
all.value1 <- read.table("stat_sampling/s_var1/allelic_values.txt", skip = 16)
points(all.value1$V3,all.value1$V4)
sum(all.value1$V3^2*all.value1$V4)
sum(all.value2$V3^2*all.value2$V4)
```


```{r}
genotype.r <- rnorm(nb.rep*2,0,1)
phenotype.r <- genotype.r[1:1000] + genotype.r[1001:2000]
var(phenotype.r)
sd(phenotype.r)
```

####Two individual
```{r}
phenotype.2s = c()
for (i in 1:nb.rep){
  my_sim <- my_sim.base
  my_sim <- setParameter(my_sim, "patch_sample_size", 2)
  my_sim@sim.name <- "s_individual"
  success <- run(my_sim, verbose = F)
  stat.ind <- loadStat(my_sim)
  phenotype.2s <- c(phenotype.2s, (stat.ind$q.meanG))
}

```

####half_population
```{r}
phenotype.0.5p = c()
for (i in 1:nb.rep){
  my_sim <- my_sim.base
  my_sim <- setParameter(my_sim, "patch_sample_size", 0.5)
  my_sim@sim.name <- "s_individual"
  success <- run(my_sim, verbose = F)
  stat.ind <- loadStat(my_sim)
  phenotype.0.5p <- c(phenotype.0.5p, (stat.ind$q.meanG))
}

```

####entire population
```{r}
phenotype.all = c()
for (i in 1:nb.rep){
  my_sim <- my_sim.base
  my_sim@sim.name <- "s_individual"
  success <- run(my_sim, verbose = F)
  stat.ind <- loadStat(my_sim)
  phenotype.all <- c(phenotype.all, (stat.ind$q.meanG))
}

```



