---
title: "Launching all test"
---

This notebook allow to launch all test in an automatic way and tell you which one fails and which one succeed.    

Due to the stochastic component of quantiNemo, some test might fail even if the component is actually working. Typically, when launching the entire set of test, 0 to 5 test might fail. If so, I recommand to relaunch the test which didn't pass, and if they fail more than twice/three time in a row, go investigate into the corresponding notebook to see where the problem comes from. 

### Defining components
```{r}
working.components =  c("cloning", "dispersal", "population_grow", "extinction", "fitness_factor", "fitness_landscape", "recombination","selection_coefficient", "selection_level", "sex_determination", "density_migration_rate", "stat_sampling",
                        "macro", "random_per_replicate","initial_genotype", "coalescence", "external_file","mutation_model","fitness_landscape_various_patch")
not.working.components = c("female_sex_allocation",  "friction", "pleiotropy")
components = c(working.components, not.working.components)
```


###Cleaning all files
```{r}
system2("rm",paste("-R ", paste(paste(components,"/", sep = ""), collapse = " ")))
system2("rm",paste("-R ", paste(paste(components,"_files","/", sep = ""), collapse = " ")))
system2("rm","output.log")
```

###function to test a component
```{r}
test <- function(component){
  res <- try(rmarkdown::render(paste(component,".Rmd", sep=""),quiet = TRUE),silent=TRUE)
  if(class(res)=="try-error"){
    cat(rep("#",50))
    cat(paste("\nSomething went wrong in the component: ",component,"\n", sep=""))
    cat(res[1])
    cat(rep("#",50), "\n \n")
  }
  else{
      cat(paste("Component: ",component," passed test \n\n", sep=""))
  }
}
```

```{r}
test("more_allele")
```


###Launching the test 
```{r}
system2("../RQuantiNemo/quantinemo.mac","--version")
for(component in working.components){
  test(component)
}
```


